Hierarchically modelling \emph{Kepler} dwarfs and subgiants to improve inference of stellar properties with asteroseismology

### 2020-11-09 paper/main.tex
Fixed typo and added back-prop. citation

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[A. J. Lyttle et al.]{
Alexander J. Lyttle,$^{1,2}$\thanks{E-mail: ajl573@student.bham.ac.uk}
Guy R. Davies,$^{1,2}$
Tanda Li,$^{1,2}$
Lindsey M. Carboneau,$^{1,2}$
\newauthor
Oliver J. Hall,$^{1,2}$
Hin Leung,$^{1,2,3}$
Harry Westwood,$^{1,2}$
William J. Chaplin,$^{1,2}$
Daniel Huber,
\newauthor
Andrea Miglio,$^{1,2}$
Martin B. Nielsen,$^{1,2}$
and To B. Confirmed
\\
% List of institutions
$^{1}$School of Physics and Astronomy, University of Birmingham, Birmingham, B15 2TT, UK\\
$^{2}$Stellar Astrophysics Centre (SAC), Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
$^{3}$School of Physics and Astronomy, University of St Andrews, North Haugh, St Andrews, KY16 9SS, UK\\
}

@@

To fit the ANN, we used a set of training data, $\boldsymbol{D}_\mathrm{train} = \{(\boldsymbol{X}_1, \boldsymbol{Y}_1) \dots (\boldsymbol{X}_{N_\mathrm{train}}, \boldsymbol{Y}_{N_\mathrm{train}})\}$ comprising $N_\mathrm{train}$ input-output pairs. We split the training data into pseudo-random batches, $\boldsymbol{D}_\mathrm{batch}$ because this has been shown to improve ANN stability and computational efficiency \citep{Masters.Luschi2018}. The set of predictions made for each batch is evaluated with an error function, $E(\boldsymbol{D}_\mathrm{batch})$, also known as the \emph{loss} which quantifies the difference between the training data and predictions. We also considered an addition to the loss called \emph{regularisation} which helps reduce over-fitting \citep{Goodfellow.Bengio.ea2016}. During fitting, the weights are updated after each batch using an algorithm called the \emph{optimizer}, back-propagating the error with the goal of minimising the loss.

@@

We obtained results for each of the models described above by sampling their posterior distributions using a Markov chain Monte Carlo (MCMC) algorithm. In particular, we used the NUTS algorithm implemented in \textsc{TensorFlow Probability} \citep[\textsc{TFP};][]{Abadi.Barham.ea2016, Dillon.Langmore.ea2017}\footnote{We interacted with the \textsc{TFP} using the now depreciated \textsc{PyMC4} package, developed as a successor to \textsc{PyMC3} \citep{Salvatier.Wiecki.ea2016}}. For each model, we produced \num{20000} samples split across \num{10} MCMC chains and computed summary statistics for the marginalised posteriors of each parameter in the model. We removed stars with problems during tuning using the Gelman-Rubin diagnostic \citep[$\hat{r}$;][]{Gelman.Rubin1992}. We used results from each model once $\hat{r} < 1.04$ for all parameters, indicating good model convergence.

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[A. J. Lyttle et al.]{
Alexander J. Lyttle,$^{1,2}$\thanks{E-mail: ajl573@student.bham.ac.uk}
Guy R. Davies,$^{1,2}$
Tanda Li,$^{1,2}$
Lindsey M. Carboneau,$^{1,2}$
\newauthor
Hin Leung,$^{1,2,3}$
Harry Westwood,$^{1,2}$
William J. Chaplin,$^{1,2}$
Oliver J. Hall,$^{4}$
\newauthor
Daniel Huber,
Andrea Miglio,$^{1,2}$
Martin B. Nielsen,$^{1,2}$
and To B. Confirmed
\\
% List of institutions
$^{1}$School of Physics and Astronomy, University of Birmingham, Birmingham, B15 2TT, UK\\
$^{2}$Stellar Astrophysics Centre (SAC), Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
$^{3}$School of Physics and Astronomy, University of St Andrews, North Haugh, St Andrews, KY16 9SS, UK\\
$^{4}$European Space Agency (ESA), European Space Research and Technology Centre (ESTEC), Keplerlaan 1, 2201 AZ Noordwijk, Netherlands\\
}

@@

To fit the ANN, we used a set of training data, $\boldsymbol{D}_\mathrm{train} = \{(\boldsymbol{X}_1, \boldsymbol{Y}_1) \dots (\boldsymbol{X}_{N_\mathrm{train}}, \boldsymbol{Y}_{N_\mathrm{train}})\}$ comprising $N_\mathrm{train}$ input-output pairs. We split the training data into pseudo-random batches, $\boldsymbol{D}_\mathrm{batch}$ because this has been shown to improve ANN stability and computational efficiency \citep{Masters.Luschi2018}. The set of predictions made for each batch is evaluated with an error function, $E(\boldsymbol{D}_\mathrm{batch})$, also known as the \emph{loss} which quantifies the difference between the training data and predictions. We also considered an addition to the loss called \emph{regularisation} which helps reduce over-fitting \citep{Goodfellow.Bengio.ea2016}. During fitting, the weights are updated after each batch using an algorithm called the \emph{optimizer}, back-propagating the error with the goal of minimising the loss \citep[see e.g.][]{Rumelhart.Hinton.ea1986}.

@@

We obtained results for each of the models described above by sampling their posterior distributions using a Markov chain Monte Carlo (MCMC) algorithm. In particular, we used the NUTS algorithm implemented in \textsc{TensorFlow Probability} \citep[\textsc{TFP};][]{Abadi.Barham.ea2016, Dillon.Langmore.ea2017}\footnote{We interacted with the \textsc{TFP} using the now deprecated \textsc{PyMC4} package, developed as a successor to \textsc{PyMC3} \citep{Salvatier.Wiecki.ea2016}}. For each model, we produced \num{20000} samples split across \num{10} MCMC chains and computed summary statistics for the marginalised posteriors of each parameter in the model. We removed stars with problems during tuning using the Gelman-Rubin diagnostic \citep[$\hat{r}$;][]{Gelman.Rubin1992}. We used results from each model once $\hat{r} < 1.04$ for all parameters, indicating good model convergence.
